Supporting Information

### 2016-08-17 portfolio/text/supp.Rnw
Supp figs

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-gg-spoke-all.pdf}
\caption{Caption here}
\label{fig:spoke-all}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid.png}
\caption{Caption here}
\label{fig:resid}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid-down.png}
\caption{Downside only}
\label{fig:resid-downside}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/strategy-year-effects.pdf}
\caption{Caption here}
\label{fig:str-yrs}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/lmer-vs-stan.pdf}
\caption{Caption here}
\label{fig:lmer-stan}
\end{center}
\end{figure}
